A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-08 doc/draft-01-stokes/02prelim.tex
cleaning up section 2,3 (done till 3.5 except last theorem)

For a given velocity field $\bu$ and pressure $p$, let $\bsigma(\bu,p)$
denote the Cauchy stress tensor, i.e.
\begin{equation}
\bsigma(\uu,p) = -p \II + 2 \be(\bu) \, ,
\end{equation}
where $\be(\bu)$ is the strain tensor given by
\begin{equation}
e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
\end{equation}
When it is clear from context, we will drop the dependence of
$\bsigma$ on $\bu$ and $p$.

We seek solutions of \cref{eq:ostokes} in the space

\begin{equation}
  A(\Omega) = \{ (\bu,p) \textrm{ s.t. } \bu \in
  \left ( C^2(\Omega)\times C^2(\Omega) \right ) \cap
  \left ( C(\bar{\Omega}) \times C(\bar{\Omega}) \right ) \, , \,
  p \in C^1(\Omega) \times C(\bar{\Omega})\} \; ,
\end{equation}
where $\Omega$ is an open domain and $\bar{\Omega}$ denotes
its closure.

@@

\begin{equation} \label{eq:doublelayer}
  \bD [\bmu] (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\xx,\yy)
  \nu_ell(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
\end{equation}
where $\bnu$ denotes the outward unit normal to the boundary.
Note that when $\xx \in \Gamma$ we obtain the same formula
for the double layer potential except that the integral should be
interpreted in the principal value sense. 
If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
where $\btau = \bmu^\bot$ is the positively oriented unit
tangent to the curve, then we have

@@

\begin{equation} \label{eq:bi_form}
  \langle \ff , \bg \rangle = \int_\Gamma \ff \cdot \bg dS \; .
\end{equation}
The definition of the adjoint used throughout the paper will be
the one induced by this form.
The adjoint of $\cD$ is of particular interest; we have
$\cD^\intercal = \cN$, where

\begin{equation}
  \cN [\bmu] = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}\nu_\ell(\xx)
  \right ) \bmu(\yy) \, dS(\yy) \; .
\end{equation}

\begin{remark}
The operators $\cD$ and $\cN$
depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
In places where it is essential to highlight this dependence, in a slight
abuse of notation, we will use the symbols $\cD(k)$ and $\cN(k)$ to 
denote this dependence. 
\end{remark}

@@

\begin{thrm} \label{thrm:rep-theorem}
  Let $\Omega$ be a bounded domain with $C^2$ boundary and let
  the pair $(\bu,p)$ satisfy the oscillatory stokes equations
  \cref{eq:ostokes} in $\Omega$. Then

  \begin{equation} \label{eq:rep-theorem}
    \bS [\bsigma(\bu,p)](\xx) - \bD[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \, , \\
    0 &\quad \xx \in \Omega^{C} \; .
    \end{cases}
  \end{equation}
\end{thrm}

@@

\begin{lem}[Jump conditions] \label{lem:jump-conds}
  Let $\bS$, $\bsigma_\bS$, $\bD$, $\cD$, and $\cN$ be
  the layer potentials and operators defined above and
  let $\Gamma$ be a sufficiently smooth domain boundary
  with outward pointing normal $\bnu$. Then, for
  a given density $\bmu$ defined on $\Gamma$,
  we have that $\bS \bmu$
  is continuous across $\Gamma$, the exterior and interior
  limits of the surface traction of $\bD \bmu$ are equal,
  and for each $\xx_0 \in \Gamma$,

  \begin{align}
    \lim_{h \downarrow 0} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
    &= \mp \frac{1}{2} \bmu(\xx_0) + \cN[\bmu](\xx_0) \\
    \lim_{h \downarrow 0} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
    &= \pm \frac{1}{2} \bmu(\xx_0) + \cD[\bmu](\xx_0)    \; .
  \end{align}
\end{lem}

@@

  Let $\Omega$ be a domain with $C^2$ boundary and $\bmu$ be
  an integrable function defined on $\Gamma$. Then
  \begin{itemize}
  \item $\cW[\cW[\bmu]] = \cW[\bmu]$,
  \item $\cW^\intercal = \cW$,
  \item $\cW[\bmu \pm 2 \cD[\bmu]] = 0$,
  \item If $\int_{\Gamma} p = 0 dS$, then
  $\cW[\bmu \pm 2 \cD^{T}[\bmu]] = 0$,
  \item $\cW[\cS[\bmu]] = 0$,
  \end{itemize}
  where the transpose is induced by the bilinear
  form \cref{eq:bi_form}.
\end{lem}

@@

\begin{remark}
Since the pressure for the oscillatory Stokes equation is only 
well-defined up to a constant in either region, we always choose
a normalization for the pressure which satisfies the conditon
$\int_{\Gamma} p dS = 0$.
\end{remark}

>>>>

For a given velocity field $\bu$ and pressure $p$, let $\bsigma(\bu,p)$
denote the Cauchy stress tensor, i.e.
\begin{equation}
\bsigma(\uu,p) = -p \II + 2 \be(\bu) \, ,
\end{equation}
where $\be(\bu)$ is the strain tensor given by
\begin{equation}
e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
\end{equation}
When it is clear from context, we will drop the dependence of
$\bsigma$ on $\bu$ and $p$.
If $\Gamma$ is the boundary of a region $\Omega$ and $\bnu$ is the outward
normal to $\Gamma$, the surface traction $\bt$ on $\Gamma$ 
is the Neumann data, i.e. 
\begin{equation}
\bt = \bsigma \cdot \bnu \, .
\end{equation}

We seek solutions of \cref{eq:ostokes} in the space
\begin{equation}
  A(\Omega) = \{ (\bu,p) \textrm{ s.t. } \bu \in
  \left ( C^2(\Omega)\times C^2(\Omega) \right ) \cap
  \left ( C(\bar{\Omega}) \times C(\bar{\Omega}) \right ) \, , \,
  p \in C^1(\Omega) \times C(\bar{\Omega})\} \; ,
\end{equation}
where $\Omega$ is an open domain and $\bar{\Omega}$ denotes
its closure.

@@

\begin{equation} \label{eq:doublelayer}
  \bD [\bmu] (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\xx,\yy)
  \nu_\ell(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
\end{equation}
where $\bnu$ denotes the outward unit normal to the boundary.
Note that when $\xx \in \Gamma$ we obtain the same formula
for the double layer potential except that the integral should be
interpreted in the principal value sense. 
If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
where $\btau = \bnu^\bot$ is the positively oriented unit
tangent to the curve, then we have

@@

\begin{equation} \label{eq:bi_form}
  \langle \ff , \bg \rangle = \int_\Gamma \ff \cdot \bg dS \; .
\end{equation}
The definition of the adjoint used throughout the paper will be
the one induced by this form.
The adjoint of $\cD$ is of particular interest; we have
\begin{equation}
  \cD^{\intercal} [\bmu] = \oint_\Gamma \left ( \TT_{\cdot,\cdot,\ell}\nu_\ell(\xx)
  \right ) \bmu(\yy) \, dS(\yy) \; .
\end{equation}

\begin{remark}
The operators $\cD$ and $\cD^{\intercal}$
depend on the Helmholtz parameter $k$ of the oscillatory Stokes equation.
In places where it is essential to highlight this dependence, in a slight
abuse of notation, we will use the symbols $\cD_{k}$ and $\cDt_{k}$ to 
denote this dependence. 
\end{remark}

@@

\begin{thrm} \label{thrm:rep-theorem}
  Let $\Omega$ be a bounded domain with $C^2$ boundary and let
  the pair $(\bu,p)$ satisfy the oscillatory stokes equations
  \cref{eq:ostokes} in $\Omega$. Let $\bt$ denote the surface
  traction associated with the velocity $\bu$. Then

  \begin{equation} \label{eq:rep-theorem}
    \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \, , \\
    0 &\quad \xx \in \Omega^{C} \; .
    \end{cases}
  \end{equation}
\end{thrm}

@@

\begin{lem}[Jump conditions] \label{lem:jump-conds}
  Let $\bS$, $\bsigma_\bS$, $\bD$, $\cD$, and $\cDt$ be
  the layer potentials and operators defined above and
  let $\Gamma$ be a sufficiently smooth domain boundary
  with outward pointing normal $\bnu$. Then, for
  a given density $\bmu$ defined on $\Gamma$,
  we have that $\bS \bmu$
  is continuous across $\Gamma$, the exterior and interior
  limits of the surface traction of $\bD \bmu$ are equal,
  and for each $\xx_0 \in \Gamma$,

  \begin{align}
    \lim_{h \downarrow 0} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
    &= \mp \frac{1}{2} \bmu(\xx_0) + \cDt[\bmu](\xx_0) \\
    \lim_{h \downarrow 0} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
    &= \pm \frac{1}{2} \bmu(\xx_0) + \cD[\bmu](\xx_0)    \; .
  \end{align}
\end{lem}

@@

  Let $\Omega$ be a domain with $C^2$ boundary and $\bmu$ be
  an integrable function defined on $\Gamma$. Then
  \begin{itemize}
  \item $\cW[\cW[\bmu]] = \cW[\bmu]$,
  \item $\cW^\intercal = \cW$,
  \item $\cW[\bmu - 2 \cD[\bmu]] = 0$,
  \item $\cW[\cS[\bmu]] = 0$,
  \end{itemize}
  where the transpose is induced by the bilinear
  form \cref{eq:bi_form}.
\end{lem}

@@
